### 2019-09-09 papers/journal/2019_ACTA_Rebuttal_Rd2.txt

% Reviewer 1:
 > My comments and concerns have been addressed in detail. Thank you.

@@

  Pt #3: 
-------- Handle by Ashutosh --------------   
  Another point that should be revised further is around 
  clarifying the contributions of this paper. The response 
  document summarizes nicely that, together with additional 
  QBF encoding, "this paper brings together all the results 
  with extended experiments and more detailed expositions for 
  the benefit of both biological and computation community." 
  However, I did not find a similar concise statement of the 
  contributions in the text. In addition, some of the stated 
  advances over previous approaches seem incremental and minor. 
  For example, for the previous CBMC-based method it is stated 
  that "...the scalability of the method was insufficient. 
  The tool was able to handle the system with just eight 
  compartments". Yet, we learn that "A typical eukaryotic 
  cell contains 9 organelles" and even one of the methods 
  presented in this paper fails for some of the experimental 
  evaluations with 7 or more compartments. The contributions 
  of this work, perhaps in the integration and evaluation of
  several methods reported previously, should be stated clearly 
  and accurately in the main text.

  Pt #4: 
-------- Handle by Ankit and Ashutosh--------------  
  A final minor point is about the use of "Synthesis" as 
  an encoding in Fig 4 and the relevant explanations. 
  Since the other problems list verification techniques 
  and solvers (e.g. BMC, SMT, QBF) and no novel synthesis 
  algorithms were developed for this problem, it would be 
  more appropriate to specify QBF as the encoding used for 
  the "VTS synthesis" problem.

% Reviewer 4:

  > Point 6 on page 3 is the same as point 4.

  Authors response: We thank the reviewer for pointing 
  this out. The two points were indeed duplicates. We 
  have now removed point 6.

  > I would argue still that the biological section has 
    unnecessary detail and could be simplified further.

  Authors response: We acknowledge that in the paper, 
  we only deal explicitly with SNARE proteins. Although 
  it is not required for an understanding of the work, 
  we feel a glimpse of the kinds of processes involved 
  in vesicle traffic, and its molecular machinery might 
  help the reader appreciate why we have built our model 
  in this particular way.

  > That the steady-state condition corresponds to the 
    biological meaning of homeostasis is repeated. This 
    only needs to be mentioned once.

  Authors response: We now state the equivalence of our 
  steady state condition and homeostasis of compartments
  only in section 2.3.2.

### 2019-09-09 papers/journal/bio.tex
Updated draft with Somya's bio updates

\subsubsection{Vesicle budding} 
The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Fig.~\ref{fig:vts}). 
%
Cargo sorting is performed by cytosolic adaptor proteins. 
%
Adaptor proteins bind to cargo molecules on the source
compartment and thereby sequester them for packaging \cite{paczkowski2015cargo}. 
%
Next, cytosolic coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins \cite{faini2013vesicle}. 
%
Coat proteins cause membrane deformation. 
%
Finally, transport vesicles bud out from the source
compartment \cite{cocucci2014dynamin}. 
%
The vesicle is now ready for transport and subsequent fusion with a target compartment.
%
%The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Fig.~\ref{fig:vts}).
%%
%Cargo sorting is performed by cytosolic adaptor proteins. 
%Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}. 
%%
%Then these adaptors bind to cargo molecules and thereby sequester them for packaging. 
%%
%Different adaptor proteins act at different compartments, for example, vesicle formation at the ER requires the adaptor sec23/24, and the AP2 adaptor is used for packaging vesicles at the plasma membrane.
%%
%
%The next step is membrane deformation, which involves cytosolic coat proteins. 
%%
%Coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins. 
%%
%These are naturally curved proteins, and their assembly on membranes leads to membrane deformation.
%%
%A single kind of coat protein can bind to multiple kinds of adaptors, thereby allowing the packaging of multiple types of cargo within the same vesicle. 
%%
%There are three major types of coat proteins: Clathrin, COP2, and COP1. These act on different compartments: the clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment: the ER and the Golgi respectively~\cite{faini2013vesicle}.
%%
%Finally, transport vesicles bud out from the source compartment~\cite{cocucci2014dynamin}.
%%
%The vesicle is now ready for transport and subsequent fusion with a target compartment.

@@

In eukaryotic cells, vesicle transfer will change the molecular composition (distinct molecule count) on both the source compartment and the target compartment. 
%
In our model, we assume that the cell is in a steady state. As a further simplification, we also assume that the incoming and outgoing flux is balanced for each of the molecular types at each compartment.
%
This is much stronger than the constraint that each molecule type entering a compartment must also leave it.
%
But, since our model is essentially binary, the two statements become equivalent. 
%
Indeed, it is well accepted that on the scale of minutes and hours the molecular composition remains the same. 
%
In this paper, we refer to the steady state of the cell (referred to as homeostasis in biological literature) as the stability condition over the annotated graph.

@@

%
%Properties of the VTS would be hindered by the same reason. 
%3-connected graphs and all possible variations of SNARE regulation rules. 
%
%The number of graphs of specified connectivity grows exponentially with the number of nodes: Table~\ref{tab:threec} shows how many 3-edge-connected graphs~\cite{a052448-oeis} exist (without parallel or self edges) as node number N increases.
\subsection{Graph connectivity is an interesting and accessible property of the VTS} 
%\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
%\noindent Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths.
%%
%The molecules of the VTS, their interactions, and modes of regulation have been worked out to a large extent through cell-biological experiments. 
%%
%But we do not know if this information is complete. In order to assess how completely we know the VTS, we need easily readable benchmarks. 
%
%One such benchmark is provided by our result about the connectivity of the VTS graph. Graph connectivity is defined as the minimum number of edges that need to be removed from an undirected graph to render it disconnected. 
%\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
Suppose we are given a particular transport graph, a particular labeling of all the compartments and edges, a particular fusion pairing matrix, and a particular regulatory model. This information is then sufficient to check the following properties, which summarise the cell-biological constraints described above:
\begin{enumerate}
	\item We can determine which molecules are active on every compartment or vesicle.
	\item For every vesicle fusing to a compartment, we can determine whether there exists an active pair (one molecule on the vesicle, one on the compartment) which drives that fusion event.
	\item For every vesicle-compartment pair where the vesicle does not fuse to the compartment, we can verify that there is no pairing of active molecules on the
	vesicle and compartment that could drive their fusion.
	\item We can verify that every molecular type entering a compartment also leaves the compartment, and also that every molecular type entering a set of compartments also leaves that set. This is the steady state condition. In the biological literature this is often referred to as “homeostasis” and is a widespread and well-accepted assumption about cellular behaviour, at least over timescales of minutes to hours \cite{mani2016stacking}.
\end{enumerate}

>>>>

\subsubsection{Vesicle budding} 
The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Fig.~\ref{fig:vts}). 
%
Cargo sorting is performed by cytosolic adaptor proteins. 
%
Adaptor proteins bind to cargo molecules on the source
compartment and thereby sequester them for packaging \cite{paczkowski2015cargo}. 
%
Membrane deformation is caused by coat proteins which are recruited by adaptor proteins \cite{faini2013vesicle}. 
%
Although here we mention only these two molecule types, many other molecules play a role in regulation and orchestration of these processes.
%Next, cytosolic coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins \cite{faini2013vesicle}. 
%
%Coat proteins cause membrane deformation. 
%
Finally, transport vesicles bud out from the source
compartment \cite{cocucci2014dynamin}. 
%
The vesicle is now ready for transport and subsequent fusion with a target compartment.
%
%The process of vesicle budding involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment (Fig.~\ref{fig:vts}).
%%
%Cargo sorting is performed by cytosolic adaptor proteins. 
%Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}. 
%%
%Then these adaptors bind to cargo molecules and thereby sequester them for packaging. 
%%
%Different adaptor proteins act at different compartments, for example, vesicle formation at the ER requires the adaptor sec23/24, and the AP2 adaptor is used for packaging vesicles at the plasma membrane.
%%
%
%The next step is membrane deformation, which involves cytosolic coat proteins. 
%%
%Coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins. 
%%
%These are naturally curved proteins, and their assembly on membranes leads to membrane deformation.
%%
%A single kind of coat protein can bind to multiple kinds of adaptors, thereby allowing the packaging of multiple types of cargo within the same vesicle. 
%%
%There are three major types of coat proteins: Clathrin, COP2, and COP1. These act on different compartments: the clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment: the ER and the Golgi respectively~\cite{faini2013vesicle}.
%%
%Finally, transport vesicles bud out from the source compartment~\cite{cocucci2014dynamin}.
%%
%The vesicle is now ready for transport and subsequent fusion with a target compartment.

@@

In eukaryotic cells, vesicle transfer will change the molecular composition (distinct molecule count) on both the source compartment and the target compartment. 
%
In our model, we assume that the cell is in a steady state. As a further simplification, we also assume that the incoming and outgoing flux is balanced for each of the molecular types at each compartment.
%
This is much stronger than the constraint that each molecule type entering a compartment must also leave it.
%
But, since our model is essentially binary, the two statements become equivalent. 
%
Indeed, it is well accepted that on the scale of minutes and hours the molecular composition remains the same. 
%
In this paper, we refer to the steady state of the cell \cite{mani2016stacking} as the stability condition over the annotated graph.

@@

%
%Properties of the VTS would be hindered by the same reason. 
%3-connected graphs and all possible variations of SNARE regulation rules. 
%
%The number of graphs of specified connectivity grows exponentially with the number of nodes: Table~\ref{tab:threec} shows how many 3-edge-connected graphs~\cite{a052448-oeis} exist (without parallel or self edges) as node number N increases.
\subsection{Graph connectivity is an interesting and accessible property of the VTS} 
%\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
%\noindent Interactions between the molecules of the VTS together produce a functional vesicle transport network, in which molecules flow between intracellular compartments using specified paths.
%%
%The molecules of the VTS, their interactions, and modes of regulation have been worked out to a large extent through cell-biological experiments. 
%%
%But we do not know if this information is complete. In order to assess how completely we know the VTS, we need easily readable benchmarks. 
%
%One such benchmark is provided by our result about the connectivity of the VTS graph. Graph connectivity is defined as the minimum number of edges that need to be removed from an undirected graph to render it disconnected. 
%\textbf{Properties of a VTS that satisfies all cell-biological constraints:} 
Suppose we are given a particular transport graph, a particular labeling of all the compartments and edges, a particular fusion pairing matrix, and a particular regulatory model. This information is then sufficient to check the following properties, which summarise the cell-biological constraints described above:
\begin{enumerate}
	\item We can determine which molecules are active on every compartment or vesicle.
	\item For every vesicle fusing to a compartment, we can determine whether there exists an active pair (one molecule on the vesicle, one on the compartment) which drives that fusion event.
	\item For every vesicle-compartment pair where the vesicle does not fuse to the compartment, we can verify that there is no pairing of active molecules on the
	vesicle and compartment that could drive their fusion.
	\item We can verify that every molecular type entering a compartment also leaves the compartment, and also that every molecular type entering a set of compartments also leaves that set. This is the steady state condition.
	% In the biological literature this is often referred to as “homeostasis” and is a widespread and well-accepted assumption about cellular behaviour, at least over timescales of minutes to hours \cite{mani2016stacking}.
\end{enumerate}

### 2019-09-09 papers/journal/intro.tex
Updated draft with Somya's bio updates

Cell biologists have made some progress by assembling a
“parts list” of molecules that drive vesicle
traffic~\cite{dacks2007evolution}.
%
The essential processes involve the creation of vesicles loaded with
cargo from source organelles, known as “budding”, and the depositing
of those vesicles and cargo into target organelles, known as “fusion”
\cite{munro2004organelle}.
%
Proteins that are called coats and the adaptors that select the cargo regulate budding.
%
The proteins that are known as SNAREs and tethers that ensure that vesicles
fuse to the correct target regulate fusion
\cite{mani2016stacking}.
%
Although we know a great deal about molecular-level details, there has
been very little work done on how such processes are integrated across
scales to build the entire vesicle traffic system (VTS).
%
We have recently attempted to use the ideas of graph theory to address
this question \cite{mani2016stacking,shukla2017discovering}.

@@

Another interesting question is the completion of the VTS \cite{synthesisGupta}. 
%
The current picture of the VTS is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and
researchers are discovering new vesicle routes every
year~\cite{nickel2018unconventional,weill2018toolbox}. 
%
Completing the VTS is a difficult task for many important reasons: 
\begin{enumerate}
	\item The core VTS is similar across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary, barlow2017seeing}, and even in different cell types within an organism can be different~\cite{stoops2014trafficking,zhou2015arp2}.
	\item Although the basic molecular machinery is the same for all vesicle fusion events, the details of regulation can be different~\cite{davletov2007regulation,di2010calcium}.
	\item Molecules can have redundant routes within the cell~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
	\item The behavior of traffic molecules in vitro is different from their behavior inside cells~\cite{furukawa2014multiple}. 
	\item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knockouts of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
        \item Lastly, interpreting experimental results can be difficult, since the behavior of traffic molecules in vitro is different from their behavior inside cells.
\end{enumerate}

>>>>

Cell biologists have made some progress by assembling a
``parts list” of molecules that drive vesicle
traffic~\cite{dacks2007evolution}.
%
The essential processes involve the creation of vesicles loaded with
cargo from source organelles, known as ``budding”, and the depositing
of those vesicles and cargo into target organelles, known as ``fusion”
\cite{munro2004organelle}.
%
Proteins that are called coats and the adaptors that select the cargo regulate budding.
%
The proteins that are known as SNAREs and tethers that ensure that vesicles
fuse to the correct target regulate fusion
\cite{mani2016stacking}.
%
Although we know a great deal about molecular-level details, there has
been very little work done on how such processes are integrated across
scales to build the entire vesicle traffic system (VTS).
%
We have recently attempted to use the ideas of graph theory to address
this question \cite{mani2016stacking,shukla2017discovering}.

@@

Another interesting question is the completion of the VTS \cite{synthesisGupta}. 
%
The current picture of the VTS is far from complete; we do not yet know how many of the cellular proteins reach their resident compartments within the cell, and
researchers are discovering new vesicle routes every
year~\cite{nickel2018unconventional,weill2018toolbox}. 
%
Completing the VTS is a difficult task for many important reasons: 
\begin{enumerate}
	\item The core VTS is similar across eukaryotes, the traffic network in different organisms \cite{richardson2015evolutionary, barlow2017seeing}, and even in different cell types within an organism can be different~\cite{stoops2014trafficking,zhou2015arp2}.
	\item Although the basic molecular machinery is the same for all vesicle fusion events, the details of regulation can be different~\cite{davletov2007regulation,di2010calcium}.
	\item Molecules can have redundant routes within the cell~\cite{shimizu2014compensatory,nakatsukasa2014nutrient}.
	 \item Interpreting experimental results can be difficult, since the behavior of traffic molecules in vitro is different from their behavior inside cells \cite{furukawa2014multiple}.
	\item It can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knockouts of traffic molecules \cite{hirst2004epsinr,mishev2013small}.

\end{enumerate}
